\documentclass[../main.tex]{subfile}
\begin{document}
Please note, on the path to you're freedom on a personal level, you will encounter may diffrent people, with diffrent views, the very first step to freedom, is to have an open mind, if you think only the way you know is right, you can never truley be free. Everyone's defition of freedom is diffrent, and has a lot of factors in play depending on the persons own experinces.

For instance, for some people they have already found there freedom, without changing anything, for instance, some people find freedom from the LGBTQ+ community, and being able to know that there is more then just them, for some it can mean having a lot of money, and being able to travel whenever they feel like in the morning, for some it's being around there friends or family, for some it's living in a flat somewhere etc.

Some common ways people see themselves as free is:
\begin{itemize}
\item Finincal security - some people like having a lot of money, and this makes them feel free.
\item Finincal insecurity - some people also enjoy the idea of having no money, they normally belive they have outlived the concept of money.
\item sexual ortitation - some people put a lot of pride into the fact that they are asexual, pan, bi, gay, lesbain etc, and this gives them freedom, and a sense of community.
\item gender/gender identiy's - some people, mostly those who are trans, or non binary take a lot of pride in there gender identity, therefore this gives them a sense of freedom.
\item kinks - Some people pride themselves on there kinks, some say they are littles, some say they are ABDL's, some say they are rope bunnies, some say they are furries etc etc. Some also pride themselves on being vanillia.
\item hobbies - everybody has hobbies, and they usally bring a sense of freedom, along with them.
\item friends + family - some people feel the most free when they are around those whom are closest to them.
\item indepndence - likewise some people feel more free when they do not have people around them, normally this brings a sense of self worth and self abilty.
\item having zero doctors visits in years - some people just dispise the doctors, so they feel the freeest when they can avoid going where possible.
\item labels - for some labels are the best thing to happen since sliced bread, these give these people a sense of security, and a sense of belonging.
\item  being labelless - some people also prefer to not have any labels over there head, they genereally see them as limiting.
\end{itemize}

As well as many others, far too many to list, the best way to know what brings someone pride, it is best to just ask them. It may also be of use to ask them why it brings them a sense of freedom, since these reasons will also vary a lot from person to person. Some people might not be, the sort of people you wish to run into, some may be amazing people to run into, howver these are all based around there relation to your own views, so someone who is not great for you, might be for someone else. People also have there places where they are most comfortable, for some that is a public space such as a pub, or there bedroom, or garden. These are all factors to take into consideration also, both for you, and when asking about others.

These facotrs can all greatly alter you're personal view of freedom.
\end{document}
