\documentclass[../main.tex]{subfile}
\begin{document}
One of the best ways of starting to get self suffcient, and off the grid, is to look at you're online presence.

For starters, i wwould setup a website, they are very simple to make, and if you host it you're self you will also have a sense of accomplishment.

I would suggest getting an old PC or a Raspberry Pi, to host, i would also suggest just keeping it simple, people go to websites to look at the content, not for the blackest of blacks, so i would suggest limiting you're JavaScript usage, this also has the added benifit of the website loading faster (next to instantly), likewise, PHP is not fit for real world devlopment, it is a prototyping language, so my suggestion would be to just go with ethier HTML or if you are lazy, like i am, markdown then convert it to HTML. as well as CSS. Doing this will take a little while to learn, normally within an afternoon or 2, you can have a amazing website. I would suggest just playing around with the diffrent tags, and seeing what they do, and likewise, play around with CSS rules, to see how they change diffrent elements on the page.

HTML and CSS tutorials can be found on \url{https://w3schools.com} which are very good, this is where most web devlopers start there life in the field.

Great so now you should have you're own slice of the internet, lets move on.

The next thing i would do is start considering you're search engine, and chances are you are using google, this is less then ideal, since google is noted for carrying out data mining, and data profiling, i would insted suggest using one of the following search engines, which repsect you're privacy \url{search.disconnect.me}, \url{startpage.com}, \url{duck.com} or \url{searchx.me}, most of these also have onion domains, more about that later on, i am personally using DuckDuckGo most of the time, however i do also use startpage, and disconnect search on occasion too.

Next i would consider your web browser, as this can play a big role in how private you are online, and how self governing you are online also. chnaces are you are using google chrome, or firefox, well google chrome can be replaced with a replacement called ungoogled chrome, it is chromuim without any contact with google. for firefox, there are forks ofit which are a bit better privacy wise, palemoon is one such example, another good example is GNU/Icecat which is a fork which includes LibreJS, and other privacy tools, there is also the TOR browser, however this is not needed as such, dispite it being the conentional way of acsessing the TOR network, other browsers such as Icecat can connect to TOR too. There are also other browsers which are not based on ethier chrome, or firefox, such as surf, witch is built upon the webkit-gtk framework, it is very small, and simple, though lacks a lot of features by defualt (however they can be patched in pretty easily), likewise there is the qute browser withich is a keyboard driven browser.

The next consdieration is social media, this is for the most part, the biggest threat to you're online presence, and making it self hosted.Here is a comparsion of social media platforms which should be avoided where ever possible, and a platform which is better for privacy, and respects you're freedom.

\begin{tabulrx}{\textwidth}{|X|X|}
	Better platform which can be used to replace the not so good one & not so good platform \\
	mumble & discord \\
	GNU ring & skype \\
	GNU social & tumblr, facebook \\
	signal & facebook messenger \\
	wickr & facebook messenger \\
	IRC & discord \\
	4chan,8chan, onionchan & reddit \\
	asktricks & a moible phone, sms \\
\end{document}

There are other things i would replace personally such as netflix for torrenting movies, pateron with librpateron, 
